\chapter{Assembly}

This chapter covers the big-picture of assembling the system and depends heavily on the following ones.
A rudimentary bill of materials can be found in \cref{bom}.

\begin{itemize}
	\item First things first: assemble a sandwich for culinary motivation.
	\item Place the base-plate into the case and drill the ten mounting holes into the bottom of the case.
	\item Take the base-plate out, we'll come back to it later on.
	\item Install the mains power socket (with switch and fuse) into the back of the case.
	\item Replace the heatsink of the head node.
	\item Install the head node into the inside of the lid of the case.
	\item Put together the frame, double check the mounting nuts sizes, count, and location.
	\item Align the frame's M5 nuts with the corresponding holes in the base-plate and fix them in place using hot glue.
	\item Install both power supplies, the switch, and the power conduit box onto the base-plate.
	\item Connect the power supplies and the switch with the power conduit box.
	\item Add the cable used for connecting the power conduit box with the mains power socket.
		Only connect it to the conduit box for now.
	\item Connect the frame to the base-plate using six M4 screws (front, left, right).
	\item Eat the sandwich.
	\item Assemble the custom circuit boards.
	\item Put together the four panels holding 4 compute nodes each.
	\item Attach a 0.5 m network cable to the switch.
		This one is used for the head node.
	\item Attach a long network cable to the switch.
		This one can be used to connect the system to a network / computer.
	\item Attach the 12 V power cable for the head node to the 12 V power supply.
	\item Attach two 0.25 m network cables and two 0.5 m network cables to the switch.
	\item Place the last panel (nodes 13--16) upside down in front of the frame-base-plate assembly.
	\item Connect the 12 V fan power cable and the 5 V compute node power cable to the panel assembly.
	\item Mount the panel assembly to the frame, the two 0.25 m network cables go in front of the panel, the other two go behind.
		Push the panel all the way to the back before tightening the screws.
	\item Connect the four network cables to the panel assembly.
	\item Repeat for the remaining three panel assemblies.
	\item Connect the power conduit to the mains power socket with the cable you almost forgot about.
	\item Lower the frame-base-plate-panel assembly into the case.
	\item Connect the head node's power and network cable.
	\item Fasten the frame-base-plate-panel assembly through the bottom of the case using M5 screws.
	\item Connect all remaining cables.
	\item Grab your coffee mug, put on some safety glasses, and hit the power button.
	\item \textit{Explosion}
	\item \dots
	\item Profit!
\end{itemize}
