\documentclass[a4paper,notitlepage,parskip=full]{scrreprt}

\title{Cluster Coffer Manual}
\author{
	Alexander Hirsch\\
	\href{mailto:alex@dps.uibk.ac.at}{\texttt{alex@dps.uibk.ac.at}}
	\and
	Daniel Gröber\\
	\href{mailto:daniel@dps.uibk.ac.at}{\texttt{daniel@dps.uibk.ac.at}}
}
\date{}

% font
\usepackage{microtype}
\usepackage[no-math]{fontspec}
	\setmainfont{TeX Gyre Termes}
	\setsansfont{TeX Gyre Heros}
	\setmonofont{Inconsolata}[Scale=0.9]
	\addtokomafont{disposition}{\rmfamily}

% page
% \usepackage[margin=1in,showframe]{geometry}
\usepackage[margin=1in]{geometry}

% colour
\usepackage{xcolor}
	\definecolor{linkcolor}{cmyk}{1.0, 0.6, 0.0, 0.56}

% links
\usepackage{hyperref}
	\hypersetup{
		colorlinks      = true,
		citecolor       = linkcolor,
		citebordercolor = linkcolor,
		linkcolor       = linkcolor,
		linkbordercolor = linkcolor!40,
		urlcolor        = linkcolor,
		pdfstartview    = {XYZ null null null},
		pdfpagemode     = UseOutlines,
	}
	\urlstyle{same}

% math
\usepackage{amsmath}

% references
\usepackage[capitalise,noabbrev]{cleveref}

% graphics
\usepackage{graphicx}
\usepackage{pdfpages}

% tables
\usepackage{longtable}
\usepackage{booktabs}

% misc
\usepackage{scrhack}

\begin{document}

\maketitle

The \textit{Cluster Coffer} is a portable, all-in-one HPC cluster designed for demonstration purposes.
Its design makes it ideal for cramped PR events.
Just place it on a level surface, plug it in, and you are ready to compute.

This document serves as a manual for assembly and maintenance.
Furthermore, similar projects can be bootstrapped from this.
Throughout the document, take note of the elegant, yet modular design.

It mainly consists of one head node, 16 compute nodes, a switch, and power distribution.

The first chapter is a step-by-step assembly guide.
Most steps require detailed information found in the following chapters.
It is recommended to read through this document from top to bottom before touching anything.

\tableofcontents

\include{assembly}
\include{metalware}
\include{electronics}
\include{software}
\include{gallery}

\appendix
\include{bom}

\end{document}
